\plaintitle

### 2017-06-06 papers/IoT2017/services.tex
no message

In this subsection, we describe the various services that are implemented in our system. %on which transactions are built and which build on transactions.
We have already discussed the distributed ledger, which permanently stores valid transactions.
Now, we will introduce anonymous communication service, mixing service for transaction anonymity, anonymous bid storage, and smart-meter based billing.\Aron{Revise list based on final organization!}

@@

\subsubsection{Billing}

The energy consumption balance $E_i^t$ of prosumer $i$ in timeslot~$t$ is
\begin{align*}
E_i^t = & \hphantom{+} \text{measured consumption} - \text{measured production} \\
 & + \text{EPA deposited by $i$} - \text{EPA withdrawn by $i$} .
\end{align*}
Notice that energy consumption assets are not necessary for billing, they are only used to enforce safety requirements.

The financial balance $F_i^t$ of prosumer $i$ in timeslot $t$, which is to be paid by the prosumer to the DSO, is
\begin{align*}
F_i^t = & \hphantom{+} \text{FA deposited by $i$ in $t$} - \text{FA withdrawn by $i$ in $t$} \\
 & + \begin{cases}
E_i^t \cdot \field{priceProduction} & \text{ if } E_i^t < 0 \\
- E_i^t \cdot \field{priceConsumption} & \text{ otherwise.} 
\end{cases}
\end{align*}

\TODO{discussion of microgrid control based on bids and trades? (update subsubsection title)}

>>>>

In this subsection, we describe the various services that are implemented in our system. %on which transactions are built and which build on transactions.
We have already discussed the distributed ledger, which permanently stores valid transactions.
Now, we will introduce anonymous communication service, mixing service for transaction anonymity, anonymous bid storage, and smart-meter based billing.

@@

\subsubsection{Smart-Meter Based Billing}
Once a prosumer has finished trading, it deposits all of its EPA, ECA, and FA to the smart meter, by transferring them to an anonymous address generated by the smart meter.
Later, during timeslot $t$, the smart meter measures the amount of energy actually consumed (or produced) by the prosumer using physical sensors.
Then, the meter can compute the prosumer's bill for timeslot $t$, which is to be paid to the DSO, as follows.

The energy consumption balance $E_i^t$ of prosumer $i$ is
\begin{align*}
E_i^t = & \hphantom{+} \text{measured net energy consumption during timeslot } t \\ %\text{measured consumption} - \text{measured production} \\
 & - \sum_{epa \,\in\, \{\text{EPA deposited by } i\}: ~ epa.\field{start} \,\leq\, epa.\field{end}} epa.\field{power} \\
 & + \sum_{epa \,\in\, \{\text{EPA withdrawn by } i\}: ~ epa.\field{start} \,\leq\, epa.\field{end}} epa.\field{power} .
% & + \text{EPA deposited by $i$} - \text{EPA withdrawn by $i$} .
\end{align*}
Notice that consumption assets are not used directly for billing, they are only used to enforce security and safety requirements.

The bill $B_i^t$ of prosumer $i$ for timeslot $t$, which is to be paid by the prosumer to the DSO, is
\begin{align*}
B_i^t = &  \text{FA withdrawn by $i$ during $t$} - \text{FA deposited by $i$ during $t$} \\
 & + \begin{cases}
- E_i^t \cdot \field{priceProduction} & \text{ if } E_i^t < 0 \\
 E_i^t \cdot \field{priceConsumption} & \text{ otherwise,} 
\end{cases}
\end{align*}
where {\field{priceProduction}} and {\field{priceConsumption}} are the prices set by the latest regulatory transactions for timeslot $t$.
